Refinements for open automata

### 2023-04-25 2021-Refinement/paper/refinementarticleV2.tex
simulation

\begin{theorem}[Refinement is a preorder]
Refinement   is reflexive  and  transitive:  it  is  a  preorder on the set of open automata.
\end{theorem}

@@

\begin{example}  Consider again the \texttt{prod-cons} and \texttt{Simprod-cons}  automata given in the examples above.  Since we have \texttt{prod-cons} $\leq_{\{\texttt{P,Q}\}}$ \texttt{simprod-cons},  hence according to Theorem \ref{thm:ContextRefinement}, we get 
\texttt{prod-cons[P/producer]} $\leq_{\{\texttt{Q}\}}$  \texttt{Simprod-cons[P/producer]}. This can be verified by comparing the behaviour of the automaton of the figure Fig.~\ref{Fig:ComposeOA} and the automaton resulting  from the composition of the \texttt{Simprod} and  \texttt{producer} automata.\qed
\end{example}

@@

As an example of the use of this theorem, consider a refined version of the producer process of Example ~\ref{Example:prodandcons} that we  refer to as $\texttt{producer}^{*}$. According to  Theorem \ref{thm:CongurenceRefinement}, we have 
\texttt{prod-cons[P/producer]} $\leq_{\{\texttt{Q}\}}$  \texttt{prod-cons[P/$\texttt{producer}^{*}$]}; as well as \texttt{Simprod-cons[P/producer]} $\leq_{\{\texttt{Q}\}}$  \texttt{Simprod-cons[P/$\texttt{producer}^{*}$]}.

>>>>

\begin{theorem}[Simulation is a preorder]
Hole-tracking simulation
   is reflexive  and  transitive:  it  is  a  preorder on the set of open automata.
\end{theorem}

@@

\begin{example}  Consider again the \texttt{prod-cons} and \texttt{Simprod-cons}  automata given in the examples above.  Since we have \texttt{prod-cons} $\leq_{\{\texttt{P,Q}\}}$ \texttt{simprod-cons},  hence according to Theorem \ref{thm:ContextRefinement}, we get 
\texttt{prod-cons[P/producer]} $\leq_{\{\texttt{Q}\}}$  \texttt{Simprod-cons[P/producer]}. 
The behaviour of \texttt{prod-cons[P/producer]} is shown Fig.~\ref{Fig:ComposeOA}.
The automaton resulting  from the composition of  \texttt{Simprod} and \texttt{producer} is bigger and not shown here. \qed
\end{example}

@@

Consequently, as the simulation is transitive \TODO{TODO Thm 4}

\begin{example}
As an example of the use of this theorem, if we design a refined version of the producer process of Example~\ref{Example:prodandcons} and call it $\texttt{producer}^{*}$. According to  Theorem \ref{thm:CongurenceRefinement}, we have 
\texttt{prod-cons[P/producer]} $\leq_{\{\texttt{Q}\}}$  \texttt{prod-cons[P/$\texttt{producer}^{*}$]}; as well as \texttt{prod-cons[P/producer]} $\leq_{\{\texttt{Q}\}}$  \texttt{Simprod-cons[P/$\texttt{producer}^{*}$]}.

\end{example}
